%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Industry Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}
    
%---------------------------------------------------------
  \cventry
    {Vice President of Photonics} % Job title
    {Luminous Computing Inc.}
    {Santa Clara, CA} % Location
    {Sept 2021 - May 2023} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Hired and led a team of 9 engineers.}
        \item {Managed project timelines, budgets, and Gannt charts to successfully achieve company milestones and goals.}
        \item {Lead 3 silicon photonics tapeout cycles, overseeing project management, optical link budgeting, layout integration, and collaboration with cross-functional teams. Delivered the first \href{https://preprints.opticaopen.org/articles/preprint/Monolithically_integrated_112_Gbps_PAM4_optical_transmitter_and_receiver_in_a_45nm_CMOS-silicon_photonics_process/22814837}{monolithically integrated electronic/photonic 112 Gbps PAM4 transceiver}}
        \item {Served as the technical interface for our silicon photonic foundries (GlobalFoundries and SilTerra). Oversaw process/stack-up development, tapeout timelines, wafer split development, alignment with foundry capabilities, and communication of test results.}
        \item {Supervised the development of 300mm electro-optical wafer probers, involving budgeting, vendor selection, and pricing negotiation.}
        % \item {Internally brought-up the Synopsys XSR SerDes IP.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Senior Photonic Engineer} % Job title
    {}
    {} % Location
    {May 2019 - Sept 2021} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Coded a custom silicon photonic design, simulation, and tapeout software infrastructure. Contributions include a python wrapper for the C++ engine, compact models for various SiPh devices, and auxiliary tools to streamline layout integration and foundry-agnostic scripting.}
        \item {Designed and simulated custom PN junction designs for Mach-Zehnder Modulators from scratch.}
        \item {Designed and laid out test circuits and design-of-experiments to characterize junction performance.}
        \item {Built the first lab setups for optical measurements, including a home-grown wafer prober and a chip tester for electro-optic measurements.}
        \item {Single-handedly performed critical measurements on prototype chips to demonstrate key IP to help secure Series A funding.}
      \end{cvitems}
    }
    
%---------------------------------------------------------
  \cventry
    {Wireless Design Engineer} % Job title
    {Apple Inc. }
    {Cupertino, CA} % Location
    {2017 - 2019} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Improved PCB design and layout to mitigate interference between co-located radios in the Apple Watch Series 3 and 4.}
        \item {Developed and maintained python infrastructure for high-throughput test and data collection in factory.}
        \item {Support new product introduction with contract manufacturers.}
        \item {Work together with vendors and internal teams to scope out new projects and reduce wireless interference by design.}
      \end{cvitems}
    }
    
%---------------------------------------------------------
  \cventry
    {Chief Technical Officer} % Job title
    {Rebeless Inc.}
    {Princeton, NJ} % Location
    {2015-2016} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Designed photonic integrated circuits for extremely wideband analog signal processing in telecom applications (microwave photonics).}
        \item {Company technology and IP was based on PhD research.}
        \item {First product concept was an in-band full-duplex RF interference canceller.}
        \item {Handled both technical development as well as investor pitches and negotiations simultaneously.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
