%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Relevant Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}
    
%---------------------------------------------------------
\cventry
{Team Leader} % Job title
{\href{https://operations.nfl.com/gameday/analytics/big-data-bowl/2024-big-data-bowl-winner-and-finalists/}{2024 NFl Big Data Bowl Winner}}
{} % Location
{Feb 29, 2024} % Date(s)
{
  \begin{cvitems} % Description(s) of tasks/responsibilities
    \item {Selected as the grand prize winner from a field of over 300 teams.}
    \item {Trained the tackle probability model and developed the tackle opportunities concept that led to the \href{https://www.kaggle.com/code/matthewpchang/uncovering-missed-tackle-opportunities}{winning submission}.}
    \item {Built the data pipeline responsible for cleaning and converting tracking data into input feature vectors for model training.}
    \item {Designed experiments to test different model architectures and optimize model hyperparameters.}
    \item {\href{https://operations.nfl.com/gameday/analytics/big-data-bowl/2024-big-data-bowl-winner-and-finalists/}{Press Release} | \href{https://www.trumedianetworks.com/expected-value-podcast/2024/3/12/matt-chang-nfl-big-data-bowl-winner}{Podcast} | \href{https://www.loom.com/share/54c67d584ee34efbb799e8dbbd551091}{Presentation} | \href{https://www.kaggle.com/code/matthewpchang/uncovering-missed-tackle-opportunities}{Full Report} | \href{https://github.com/mpchang/uncovering-missed-tackle-opportunities}{Code}}
  \end{cvitems}
}

%---------------------------------------------------------

  \cventry
    {Vice President of Photonics} % Job title
    {Luminous Computing Inc.}
    {Santa Clara, CA} % Location
    {Sept 2021 - May 2023} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Recruited and lead an engineering team of 9 engineers.}
        \item {Lead 3 chip design cycles. Delivered the first \href{https://preprints.opticaopen.org/articles/preprint/Monolithically_integrated_112_Gbps_PAM4_optical_transmitter_and_receiver_in_a_45nm_CMOS-silicon_photonics_process/22814837}{monolithically integrated electronic/photonic 112 Gbps PAM4 transceiver}}
        \item {Managed project timelines, deparatment budget, and Gantt charts to successfully achieve company milestones and goals.}
        \item {Coded a custom silicon photonic design, simulation, and tapeout software infrastructure.}
        \item {Helped built the lab from scratch, including a home-grown 300mm electro-optical wafer prober.}
        \item {Single-handedly performed critical measurements on prototype chips to demonstrate key IP to help secure Series A funding.}
        % \item {Internally brought-up the Synopsys XSR SerDes IP.}
      \end{cvitems}
    }
    
%---------------------------------------------------------
  \cventry
    {Wireless Design Engineer} % Job title
    {Apple Inc. }
    {Cupertino, CA} % Location
    {2017 - 2019} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developed and maintained python infrastructure for high-throughput test and data collection in factory for the Apple Watch Series 3 and 4}
        \item {Support new product introduction with contract manufacturers.}
        \item {Collaborated with vendors and internal teams to scope out new projects and reduce wireless interference by design.}
      \end{cvitems}
    }
    
%---------------------------------------------------------
  \cventry
    {Chief Technical Officer} % Job title
    {Rebeless Inc.}
    {Princeton, NJ} % Location
    {2015-2016} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Designed photonic integrated circuits for extremely wideband analog signal processing in telecom applications (microwave photonics).}
        \item {Company technology and IP was based on PhD research.}
        \item {Handled both technical development as well as investor pitches and negotiations simultaneously.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
